A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-25 sections/Related.tex
RW lists of judgments

\paragraph{Ordered Contexts in Type Inference}

\paragraph{Lists of Judgements in Unification}

>>>>

\paragraph{Ordered Contexts in Type Inference}
Gundry et al.~\cite{gundry2010type}

\paragraph{Lists of Judgements in Unification}
Some work~\cite{Reed2009,Abel2011higher} adopts a similar idea to this paper
in dependently typed inference and reconstruction.
Their algorithms collect unification constraints and simplify them progressively in a single-step style.
In comparison, our algorithm mixes variable declarations with judgments,
resulting in a simpler judgment form,
while processing them in a similar way to those algorithms.
A detailed discussion is in Section~\ref{sec:overview:list}.
